### 2019-11-30 report/05-stability.Rmd
structure project 1 and 2

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
```
```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))

@@

plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)

```{r}
myload(biomass_ts_sax, dir = mypath("data"))
p_bbb_stab_div <- stab_div_basin %>%
  mutate(station = as.character(station)) %>%
  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
  filter(sax == "bbb") %>%
  ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
  )

@@

plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 2)
```

```{r temp-grp}
myload(habitat_pressure, dir = mypath("report"))

@@

@@

@@

```{r}
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))

```{r}
sync_com_troph <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  rename(species = sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
```

```{r}
sync_com_troph %>%
  filter(troph_group != 1) %>%
  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

```{r sd-avg-div}
fit <- stat_poly_eq(
  formula = y ~x,
  eq.with.lhs = "italic(hat(y))~`=`~",
  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
  parse = TRUE)

ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'loess', se = F) +
  #fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- sync_com_troph %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'loess', se = FALSE) +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

@@

Part of the solution

```{r}
formula <- y ~ x #needed for stat_poly_eq
sync_com_troph %>%
  ggplot(aes(x = bm_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10() +
  scale_x_log10() +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
      biomass (g)")
```

```{r, fig.dim = c(7, 14)}
sync_com_troph %>%
  select(troph_group:cv_com, div_st) %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = div_st, y = stab)) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(x = "Trophic species diversity", y = "Stability component") +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
```

```{r, fig.dim = c(10, 7)}
synchrony %>%
  left_join(select(temporal_community_metrics, station, richness_med), by =
    "station") %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_med, y = stab)) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(x = "Species diversity", y = "Stability component") +
  geom_point() +
  facet_grid(rows = vars(comp), scales = "free_y")
```

@@

```{r}
sync_com_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, species) %>%
  summarise(
    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
    sum_cbt_sync = sum(abs(cbt_sync))
    ) %>%
  arrange(desc(sum_cbt_cv_com)) %>%
  slice(1:10) %>%
  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
  ggplot(aes(y = contrib, x = species)) +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
```

```{r var-cbt, fig.dim = c(10, 7)}
var_cbt <- sync_com_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, station) %>%
  summarise(
    var_cbt_cv_com = var(cbt_cv_com),
    var_cbt_cv_sp = var(cbt_cv_sp),
    var_cbt_sync = var(cbt_sync)
    ) %>%
  gather(comp, contrib, var_cbt_cv_com:var_cbt_sync) %>%
  left_join(select(cv_bm_div_troph_grp, station, troph_group, div_st),
    by = c("station", "troph_group"))

  var_cbt %<>%
    nest() %>%
    mutate(plot = map2(data, troph_group, function(.data, m_title){
	.data %>%
	ggplot(aes(y = contrib, x = div_st)) +
	  geom_point() +
	  scale_x_log10() +
	  facet_wrap(facets = ~comp, scales = "free_y") +
	  labs(title = paste0(m_title))
}
    )
    )

plot_grid(plotlist = var_cbt$plot, ncol = 2)
```

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload( trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

```{r}
synchrony %>%
  left_join(hab_type, by = "station") %>%
  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
  ggplot(aes(x = richness_med, y = 1/cv_com)) +
  geom_point() +
  geom_smooth(method = "auto") +
  facet_grid(cols = vars(hab_type))
```

```{r}
synchrony %>%
  left_join(hab_type, by = "station") %>%
  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
  ggplot(aes(x = richness_med, y = 1/cv_com)) +
  geom_point() +
  geom_smooth(method = "auto")
```

```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))

@@

plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)
```

```{r, fig.dim = c(8, 7)}
myload(biomass_ts_sax, dir = mypath("data"))
p_bbb_stab_div <- stab_div_basin %>%
  mutate(station = as.character(station)) %>%
  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
  filter(sax == "bbb") %>%
  ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
  )

@@

plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 1)
```

```{r}
myload(habitat_pressure, dir = mypath("report"))
```

```{r bimod-stab-div, fig.dim = c(7, 16), fig.cap = "Relationship between stability and diversity by spliting dataset in two according to an environmental variable. The threshold for the dataset split is the median of the environmental variable."}
plot_bin_stab_div <- function (env = NULL) {

  habitat_pressure$env_bin <- ifelse(
    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
    "inf", "sup")
  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
  habitat_pressure %>%
    left_join(stab_div_basin, by = "station") %>%
    ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
    geom_point() +
    facet_grid(cols = vars(env_bin)) +
    stat_poly_eq(
      formula = y ~ x,
      eq.with.lhs = "italic(hat(y))~`=`~",
      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
      parse = TRUE) +
    geom_smooth(method = "lm", formula = y ~ x) +
    ggplot2::scale_color_manual(
      labels = troph_group_labeller(),
      values = c("blue", "green", "red"),
      name = "Trophic level"
    ) +
  labs(title = env, x = "Average species richness", y = "Biomass stability") +
  theme(legend.position = "none")
}

#width_river_mean avg_depth_station_mean
env <- c("width_river_mean", "avg_depth_station_mean", "lat",
  "temperature_med", "flow_med", "d_source", "DBO_med", "nitrates_med")
mult_plot_stab_div_bin <- map(env, ~plot_bin_stab_div(env = .x))

plot_grid(plotlist = mult_plot_stab_div_bin, ncol = 2)
```

The relationship between stability and species diversity (Figure
\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
place where the ANG is the most present. The ANG were effectively more abundant
in the latter station (Figure: \@ref(fig:ang-map-bio)).

```{r ang-map-bio, include = FALSE}
ang_bm <- network_analysis %>%
  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  filter(species == "ANG") %>%
  group_by(station) %>%
  summarise(cv_biomass = sd(biomass) / mean(biomass),
    biomass = mean(biomass))

mult_plot_ang_env <- map(env, function(x) {

  habitat_pressure$env <- habitat_pressure[[x]]

  ang_bm %>%
    left_join(habitat_pressure[, c("station", "env")], by = "station") %>%
    ggplot(aes(x = env, y = biomass)) +
    geom_point() +
    stat_poly_eq(
      formula = y ~ x,
      eq.with.lhs = "italic(hat(y))~`=`~",
      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
      parse = TRUE) +
    geom_smooth(method = "loess", formula = y ~ x) +
    scale_y_log10() +
    labs(x = x, y = "Average biomass of ANG (g)")

  })
plot_grid(plotlist = mult_plot_ang_env)
```

```{r, fig.dim = c(10, 5)}
myload(hab_type, dir = mypath("report"))
stab_div_basin %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(y = biomass_stab, x = richness_avg, color = troph_group)) +
  geom_point() +
  facet_grid(cols = vars(hab_type)) +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  scale_y_log10() +
  scale_x_log10() +
  labs(title = "Stability - Div by habitat type",
    x = "Average species richness (log10)", y = "Biomass stability (log10)")
```

```{r}
model_enrich_temp <- stab_div_basin %>%
  left_join(hab_type, by = "station") %>%
  left_join(habitat_pressure[,c("station", "temperature_med", "temperature_cv", "DBO_med", "DBO_cv")],
    by = "station") %>%
  na.omit() %>%
  group_by(troph_group, hab_type) %>%
  mutate(
    log_rich = log10(richness_avg),
    temp_res = resid(lm(temperature_med ~ log_rich)),
    dbo_res = resid(lm(DBO_med ~ log_rich)),
  ) %>%
  nest() %>%
  mutate(
    corel = map(data, function(x) {
      div_temp <- cor(x = x$richness_avg, y = x$temp_res, method = c("spearman"))
      div_dbo <- cor(x = x$richness_avg, y = x$dbo_res, method = c("spearman"))
      data.frame(div_temp = div_temp, div_dbo = div_dbo)
      }
     ),
    model = map(data, ~lm(log10(biomass_stab) ~
	log_rich  + log_rich:temp_res + log_rich:dbo_res + log_rich:temp_res:dbo_res, data = .x)),
    colinearity = map(model, ~enframe(car::vif(.x))),
    coefs = map(model, ~tidy(.x)),
    sumup = map(model, ~glance(.x))
  )

unnest(model_enrich_temp, coefs) %>%
  mutate_at(vars(estimate, std.error, statistic), ~round(., 2)) %>%
  rename(est = estimate, error = std.error,
    stat = statistic, grp = troph_group) %>%
  kable %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r}
unnest(model_enrich_temp, colinearity)

@@

```{r}
stab_div_troph %>%
  select(station, troph_group, biomass_avg) %>%
  spread(troph_group, biomass_avg) %>%
  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(x = hab_type, y = bm_h_m)) +
  geom_boxplot() +
  labs(x = "Type of river", y = "Proportion of biomass in the high trophic group")
```

```{r}
div_troph_col <- stab_div_troph %>%
  select(station, troph_group, richness_avg) %>%
  spread(troph_group, richness_avg)

stab_div_troph %>%
  select(station, troph_group, biomass_stab) %>%
  left_join(hab_type, by = "station") %>% 
  left_join(div_troph_col, by = "station") %>%
  ggplot(aes(x = `2`, y = `3`)) +
  geom_point(aes(size = log10(biomass_stab), color = log10(biomass_stab))) +
  facet_grid(cols = vars(troph_group), rows = vars(hab_type))
```

```{r}
#TODO: Update cor_troph_group 
myload(cor_troph_group, dir = mypath("data"))
cor_troph_group %>%
  left_join(hab_type, by = "station") %>%
  filter(!is.na(hab_type)) %>%
  ggplot(aes(x = hab_type, y = cor_troph)) +
  geom_boxplot() 
```

TODO: may be that the altitude station misses the really big fishes that
stabilizes the communities. Look at dist of biomass (biomass avg by station and the shape of biomass dist).

```{r}
myload(network_metrics, dir = mypath("data", "classes"))
avg_troph_lvl <- network_metrics %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  filter(troph_group != 1) %>%
  arrange(opcod, troph_group) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(opcod, troph_group) %>%
  mutate(w_troph_lvl = troph_level * biomass / sum(biomass)) %>%
  summarise(avg_t_lvl = sum(w_troph_lvl))%>%
  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
  group_by(station, troph_group) %>%
  summarise(avg_t_lvl = mean(avg_t_lvl))

avg_troph_lvl %>%
  left_join(select(stab_div_troph, station, troph_group, richness_avg), by = c("station", "troph_group")) %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(x = richness_avg, y = avg_t_lvl)) +
  geom_point() +
  facet_grid(hab_type~troph_group) +
  stat_poly_eq(
    label.x = "right",
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x)
```

@@

```{r}
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))
```

```{r}
cbt_sync_troph_without_ang <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  rename(species = sp_class) %>%
  mutate(ang_logic = ifelse(!is.na(str_match(species, "ANG")[,1] == "ANG"),
      TRUE, FALSE)) %>%
  filter(troph_group != 1, ang_logic != TRUE) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(stab_div_basin, by = c("station", "troph_group"))
```

```{r stab-ang, fig.dim = c(10, 7)}
cbt_sync_troph_without_ang %>%
  mutate(stab_without_ang = 1/cv_com) %>%
  rename(stab_with_ang = biomass_stab) %>%
  filter(troph_group != 1) %>%
  select(station, troph_group, richness_avg, stab_with_ang, stab_without_ang) %>% 
  gather(stab_type, stab, stab_with_ang, stab_without_ang) %>%
  ggplot(aes(x = richness_avg, y = stab, color = troph_group)) +
  geom_point() +
  facet_grid(cols = vars(stab_type)) +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

@@

```{r}
sync_troph <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  select(-sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(opcod, troph_group, species) %>%
  summarise(
    troph_level = sum(troph_level * biomass /sum(biomass)),
    biomass = sum(biomass)
  ) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>% 
  unnest(sync)

cbt_sync_troph <- sync_troph %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(select(temporal_community_metrics, station, richness_avg,
      biomass_avg), by = "station") %>%
  rename(bm_st = biomass_avg, div_st = troph_sp_nb_avg)
```

```{r sd-avg-div}
fit <- stat_poly_eq(
  formula = y ~ x,
  eq.with.lhs = "italic(hat(y))~`=`~",
  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
  parse = TRUE)

ymax <- max(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F) +
  fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  scale_x_log10() +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- cbt_sync_troph %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  scale_x_log10() +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

@@

```{r}
ymax <- max(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F) +
  fit +
  facet_grid(cols = vars(troph_group), rows = vars(hab_type)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  scale_x_log10() +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- cbt_sync_troph %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  fit +
  facet_grid(cols = vars(troph_group), rows = vars(hab_type)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  scale_x_log10() +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

plot_grid(p_sd, p_bm, ncol = 1)
```

```{r}
formula <- y ~ x #needed for stat_poly_eq
cbt_sync_troph %>%
  ggplot(aes(x = bm_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10() +
  scale_x_log10() +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
      biomass (g)")
```

```{r, fig.dim = c(10, 10)}
u_hab <- unique(hab_type$hab_type)
p_test <- map(u_hab, function(x){
cbt_sync_troph %>%
  select(troph_group:cv_com) %>%
  left_join(stab_div_basin, by = c("station", "troph_group")) %>%
  left_join(hab_type, by = "station") %>%
  filter(hab_type == x) %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_avg, y = stab)) +
  geom_smooth(method = "lm", se = FALSE) +
  stat_poly_eq(
    label.x = "right",
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(title = x, x = "Average species richness", y = "Stability component") +
  scale_x_log10() +
  scale_y_log10() +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")

      })
plot_grid(plotlist = p_test)
```

```{r, fig.dim = c(10, 7), include = FALSE}
synchrony %>%
  left_join(select(temporal_community_metrics, station, richness_med), by =
    "station") %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_med, y = stab)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Species diversity", y = "Stability component") +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  facet_grid(rows = vars(comp), scales = "free_y")
```

@@

```{r cbt-top, fig.cap = "Contribution of species to the different facets of stability. Positive contribution values mean that the species contributes negatively to the metric."}
top_contrib_sp <- cbt_sync_troph %>%
  unnest(contrib) %>%
  group_by(station, troph_group) %>%
  mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
  group_by(troph_group, species) %>%
  summarise(
    avg_cbt_cv_com_n = mean(cbt_cv_com_n),
    avg_cbt_cv_com = mean(cbt_cv_com),
    avg_cbt_cv_sp = mean(cbt_cv_sp),
    avg_cbt_sync = mean(cbt_sync),
    avg_abs_cbt_cv_com = mean(abs(cbt_cv_com))
    ) %>%
  arrange(desc(abs(avg_cbt_cv_com_n))) %>%
  slice(1:10)

p_top_contrib_sp <- map(c(2, 3), function(x){

  mask <- top_contrib_sp$troph_group == x 
  top_sp <- unique(top_contrib_sp[mask,]$species)

  cbt_sync_troph %>%
    unnest(contrib) %>%
    group_by(station, troph_group) %>%
    mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
    filter(species %in% top_sp, troph_group == x) %>%
    gather(comp, contrib, cbt_cv_com_n, cbt_cv_com:cbt_sync) %>%
    ggplot(aes(y = contrib, x = species)) +
    geom_violin() +
    facet_grid(rows = vars(comp), scales = "free_y") +
    labs(title = x)
    })
plot_grid(plotlist = p_top_contrib_sp)
```

The figure \@ref(fig:cbt-top), left panel) shows that for the trophic group 2,
TRF, LOF and GOU were the species that contributes the most to the the CV of the
community and to its components (CVsp and synchrony). For the 3 trophic group
(Figure \@ref(fig:cbt-top), right panel), the TRF, ANG and CHE contribute the
most to stability and its facets. Interestingly, the contribution of the species
to the community CV were quite asymetric toward negative values, meaning that
species which contributes the most tend to stabilize more than destabilize
communities. The reason was that the variance of contribution decreases with
species diversity (Figure \@ref(fig:var-cbt)), meaning that each species
contributes less and less. Two reasons might explain that: (1) the biomass
distribution of communities became more even with the increase of species
number, (2) the population stability converges.  Apparently the eveness of
biomass distribution does not change with species diversity (figure
\@ref(fig:even-sdcv-div), A). And the standard deviation of species CV decreases
with species richness (figure
\@ref(fig:even-sdcv-div), A).

```{r var-cbt, fig.dim = c(10, 7)}
var_cbt <- cbt_sync_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, station) %>%
  summarise(
    var_cbt_cv_com = var(cbt_cv_com),
    var_cbt_cv_sp = var(cbt_cv_sp),
    var_cbt_sync = var(cbt_sync)
    ) %>%
  gather(comp, contrib, var_cbt_cv_com:var_cbt_sync) %>%
  left_join(select(stab_div_basin, station, troph_group, richness_avg),
    by = c("station", "troph_group"))

  var_cbt %<>%
    nest() %>%
    mutate(plot = map2(data, troph_group, function(.data, m_title){
	.data %>%
	ggplot(aes(y = contrib, x = richness_avg)) +
	  geom_point() +
	  scale_x_log10() +
	  facet_grid(rows = vars(comp), scales = "free_y") +
	  labs(title = paste0(m_title))
}
    )
    )
plot_grid(plotlist = var_cbt$plot, ncol = 2)
```

#### Statistical averaging

```{r eveness-div}
pielou <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  select(-sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(opcod, troph_group, species) %>%
  summarise(
    troph_level = sum(troph_level * biomass /sum(biomass)),
    biomass = sum(biomass)
  ) %>%
  group_by(troph_group, opcod) %>%
  mutate(rel_bm = biomass / sum(biomass)) %>%
  summarise(
    richness = n(),
    shannon = vegan::diversity(biomass, index = "shannon"),
    pielou = shannon / log(n())
  )

p_pielou <- pielou %>%
  left_join(select(op_analysis, station, opcod), by = "opcod") %>%
  group_by(station, troph_group) %>%
  summarise(richness_avg = mean(richness), pielou_med = median(pielou)) %>%
  left_join(hab_type, by = c("station")) %>%
  ggplot(aes(x = richness_avg, y = pielou_med, color = hab_type)) +
  #scale_x_log10() +
  geom_point() +
  facet_grid(~troph_group) +
  stat_poly_eq(
    label.x = "right",
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "loess", formula = y ~ x, se = FALSE) +
  labs(x = "Avg species richness", y = "Avagerage evenness of biomass")

p_pielou
```

```{r even-sdcv-div}
var_sp <- sync_troph %>%
  mutate(var_sp = map(var_sp, enframe)) %>%
  unnest(var_sp) %>%
  rename(species = name, var_bm = value) %>% 
  select(station, troph_group, species, var_bm)
avg_sp <- sync_troph %>%
  mutate(avg_sp = map(avg_sp, enframe)) %>%
  unnest(avg_sp) %>%
  rename(species = name, avg_bm = value) %>% 
  group_by(station, troph_group) %>%
  mutate(rel_bm = avg_bm / sum(avg_bm)) %>%
  ungroup() %>%
  select(station, troph_group, species, avg_bm, rel_bm)
cv_bm_sp <- left_join(avg_sp, var_sp, by = c("station", "troph_group", "species")) %>%
  mutate(cv = sqrt(var_bm) / avg_bm, var_bm = NULL) %>%
  rename(bm = avg_bm)

p_cv_sp_div <- map(unique(hab_type$hab_type), function(hab) {
